%! TEX root=../main.tex

\section{Responses}
  \subsection{Response 1}
    \begin{quotation}
      The first thing I've begun to work on in my communication is clarity in
        speech. In this movie clip it shows Ace Ventura speaking very quickly
        while keeping his speech clear. It shows multiple scenes where he takes
        a deep breath and quickly answers their questions fully while not
        stuttering or making a mistake. He stays confident in his tone. One
        thing I can learn from this is to remember to take a deep breath. This
        helps you to stay calm so that you can stay clear in your speech.

      Another thing I have been working on is managing emotions in speech. In
        this video clip Peter goes through a couple of things that for a lot of
        people would have caused an emotional outbreak. For one, he was talked
        to by both bosses when neither of them seemed to listen to him, and
        another coworker was playing the radio which seemed to annoy Peter.
        With all of these things, Peter could have reacted with anger or
        frustration. Instead, he stayed calm and moved on. He didn't allow the
        things to bother him too much and moved on which is something I could
        learn to do.

      The final thing I could have worked more on was nonverbal communication
        skills. This was something I didn't focus enough on. In the first scene
        of this clip, Lucy struggles with her nonverbal communication skills
        but after each try gets a little better. She's working on her facial
        expressions and by smiling is able to conceal her emotions a little.
        Something I learned from this is it can be difficult sometimes, but it
        helps to try and smile through it.
    \end{quotation}

    \paragraph{This is a response to Julayne Kilcullen on Post ID 43614390}
      Amazing response to the discussion prompt, Julayne! It is unfortunate that
        we did not get a chance to get to know each other (even a little,
        I do not even recall us reading each other's respective discussion
        posts)! I see you had mentioned that you did not necessarily work on
        \textit{nonverbal communication skills} as much as many other
        interpersonal communication skills we had discussed throughout the
        course. It is hard to compare your ability to that of Lucy's right now,
        considering the state of the pandemic we are suffering though right now!

      You mentioned that that smiling through a tough time was a good way to
        conceal one's own emotions when in conversation with his/her/their
        peers, but what about like now --- during the Coronavirus COVID-19
        Pandemic? It is no longer possible to smile though something to get
        the idea across to others that everything is ``okay'', with the usage
        of masks (finally) rising in public places. The \textit{eyes} have
        become even more important than ever, would you agree?
